---
title: "tirefittingr Notebook"
output:
  html_notebook: default
  html_document:
    df_print: paged
  pdf_document: default
---


Disclaimer: All data and fit curves shown in this notebook are fictional. 

THERE IS NO WARRANTY FOR THE PROGRAM, TO THE EXTENT PERMITTED BY
APPLICABLE LAW.  EXCEPT WHEN OTHERWISE STATED IN WRITING THE COPYRIGHT
HOLDERS AND/OR OTHER PARTIES PROVIDE THE PROGRAM "AS IS" WITHOUT WARRANTY
OF ANY KIND, EITHER EXPRESSED OR IMPLIED, INCLUDING, BUT NOT LIMITED TO,
THE IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR
PURPOSE.  THE ENTIRE RISK AS TO THE QUALITY AND PERFORMANCE OF THE PROGRAM
IS WITH YOU.  SHOULD THE PROGRAM PROVE DEFECTIVE, YOU ASSUME THE COST OF
ALL NECESSARY SERVICING, REPAIR OR CORRECTION.


# Install
### Install R and RStudio
see the readme.md file in the root directory. 
https://github.com/fsaer/tirefittingr

### Install tirefittingr
Make sure you have downloaded and installed the package if you haven't already.
Installing only needs to be done once on a computer.

```{r eval=FALSE}
install.packages("devtools")
devtools::install_github("fsaer/tirefittingr") 

install.packages("plotly") #now is also the time to install plotly if you haven't already
```

# Load Packages
This must be done every r-session, so this code is often
at the top of every script.
```{r message=FALSE, warning=FALSE, include=TRUE}
library(tirefittingr)
library(plotly)
```

# Settings
We are going to speed up the solver a bit for this example. This will reduce the
quality of the fit.
```{r}
    options(
        tirefittingr.iParallelCores = 1,
        tirefittingr.iEvolIterMax = 30, 
        tirefittingr.iDataPoints = 3000,
        tirefittingr.sSavePlotPath = FALSE,
        tirefittingr.bPlotRunConditions = TRUE,
        tirefittingr.sSummaryExportPath = NA)
```

At a minimum, we need to set the options telling the program whether we are 
fitting we need to set the starting population and tell it which fitting 
equation to use.
```{r}
#Required options
#options(tirefittingr.sdfStartPop = "dfStartParFY")
#options(tirefittingr.sfFittingFunction = "FYPurePacejka2002")

# To save time, the function below will set the above options for us, as 
# well as a pre-processing function and plotting function specific to FY.
setFYPure2002()

# #If we wanted to analyze FX, we could do the following
# setFXPure2002.wIA()

```
Now we are ready to use the tire fitting function. 

# Fitting
For this example, we are using 2 built in data sets of fictious data
```{r}
dfFitSummary = fitTires(c("ABCrun1LatPreProccessed", "ABCrun2LatPreProccessed"))
```
After fitting, we can look at the output plots. In the run conditions plots, 
we can check that our tire got up to temperature, that it actually contains
IA sweeps, and the pressure is what we expected. 

In the goodness of fit plots, we can see how closely our fitted curve matches
the raw data. 

# Using fitTires()
Running fitTires() without any arguments will open a dialog box to pick files. 
Make sure if you have setFYPure2002, then you are selecting FY files or vice 
versa!
```{r eval=FALSE, include=TRUE}
setFYPure2002() #setFXPure2002.wIA()

dfFitSummary = fitTires()
```

As shown earlier, fitTires, can accept names of data frames that exist in memory
```{r eval=FALSE, include=TRUE}
setFYPure2002() #setFXPure2002.wIA()


dfFitSummary = fitTires("ABCrun1LatPreProccessed")
dfFitSummary = fitTires(c("ABCrun1LatPreProccessed", "ABCrun2LatPreProccessed"))
#c() joins objects into a vector
```

Last, but **most importantly**, fitTires() can **accept file paths**
```{r eval=FALSE, include=TRUE}
setFYPure2002() #setFXPure2002.wIA()

#Always use forward slashes in file paths in R!
dfFitSummary = fitTires("C:/users/fsaer/data/rawData1.dat")
dfFitSummary = fitTires(c("C:/users/fsaer/data/rawData1.dat", 
                          "C:/users/fsaer/data/rawData2.dat"))

```

We can also pass in a vector of **names** of the tire files in, to help us remember 
what they are later.
```{r eval=FALSE, include=TRUE}
setFYPure2002() #setFXPure2002.wIA()

dfFitSummary = fitTires("ABCrun1LatPreProccessed", "ABC Tire on 13in Rim")
dfFitSummary = fitTires(c("ABCrun1LatPreProccessed", "ABCrun2LatPreProccessed"), 
                    c("ABC Tire1", "ABC Tire2" ))

```

We were storing our results in dfFitSummary. We can view these by clicking on 
the variable name in the environment window (usually top right), or with the 
command `View(dfFitSummary)`. 

We can also save this to a file with the following.
```{r eval=FALSE, include=TRUE}
#Always use forward slashes in file paths in R!
write.csv(dfFitSummary, "C:/TireFittingSummary.csv")

```

We could have automatically saved
to a csv file by setting option tirefittingr.sSummaryExportPath equal to a 
string of a folder path before running fitTires().
```{r eval=FALSE, include=TRUE}
print(getwd()) #get the working directory

#enter a full file path using forward slashes / not backslashes.
#options(tirefittingr.sSummaryExportPath = "C:/users")
options(tirefittingr.sSummaryExportPath = getwd()) 
fitTires()
```

For a full list of options see the help file for the fitTires() function:
```{r eval=FALSE, include=TRUE}
?fitTires
```

# Plotting Curves
Feel free to switch to matlab or excel/vba from here. The equations 
used are available on github at fsaer/tirefittingr/R/Magic.R or 
https://github.com/fsaer/tirefittingr/blob/master/R/Magic.R.

Now let's compare our two tires in basic FY vs Slip Angle plots. 
First, we will decide what sweeps of parameters will will be plotting.
Our pacejka equation requires `SA`, `FZ`, and `IA`, so we have to include them.
```{r}
#Using the results from:
# setFYPure2002()
# dfFitSummary = fitTires(c("ABCrun1LatPreProccessed", "ABCrun2LatPreProccessed"))

SAplot = seq(from = -12, to = 12, by = 0.05) #Slip angle in degrees
IAPlot = 0 #inclination angle in degrees
# FZ0Plot = -1600 #Nominal FZ value. -1600 is a good number. 
FZPlot = c(-250, -750, -1200) #FZ in Newtons
IAPlot = 0
    
```

The easiest way to create data frames that we can plot is by using the 
createFitDataFrame function. This function will evaluate our fitting function, 
in this case FYPurePAcejka2002, at every different combination of our SA, IA, 
and FZ inputs. 

We can learn more about this function with
```{r eval = FALSE}
?createFitDataFrame
```

After creating our data we'll create a matrix that is easy to plot
```{r}
mGridPlot = createFitDataFrame(FYPurePacejka2002, "parameters", SA = SAplot, 
    FZ = FZPlot, IA = IAPlot, parameters = dfFitSummary[1, 9:ncol(dfFitSummary)])
```

Create a blank plot and set the legend at the top.
```{r}
myPlot = plotly::layout(plot_ly(), 
                        legend = list(orientation = 'h', x = 0, y = 1.15))
```

Add markers to the plot
```{r}
myPlot = add_markers(myPlot, data = mGridPlot, x = ~SA, y = ~FY, 
    name = dfFitSummary[1, 1], marker = list(color = "blue"))
show(myPlot)
```

Let's create a second data frame for our second data set, then plot it.
```{r}
#Create a matrix that is easy to plot
mGridPlot2 = createFitDataFrame(FYPurePacejka2002, "parameters", SA = SAplot, 
    FZ = FZPlot, IA = IAPlot, parameters = dfFitSummary[2, 9:ncol(dfFitSummary)])

#Add markers to the plot
myPlot = add_markers(myPlot, data = mGridPlot2, x = ~SA, y = ~FY, 
    name = dfFitSummary[2, 1], marker = list(color = "red"))
show(myPlot)
    
```


While a better splitting app is currently 
being developed, the splitTireData function works. It can do multiple files 
very quickly. The new split files will be saved in the same folder that the 
original files were in.

```{r eval = FALSE}
#Open window to pick files
lRunNamesSplit = splitTireDataAndSave(P = 6.894*c(8,10,12,14), verbose = TRUE)
# 
#Input file paths, use forward slashes in file paths in R!
#lRunNamesSplit = splitTireDataAndSave(c("C:/file1.dat", "C:/file2.dat"),
                               P = 6.894*c(8,10,12,14), verbose = TRUE)

```


